# Reading Data

Data can be read into R from many sources.

## Read from csv
```{r, eval=FALSE}
df <- read_csv("path/to/file.csv")
```

## Read from xlsx
Excel xlsx files can be imported using the `read.xlsx` function from the `xlsx` package.
```{r, eval=FALSE}
df <- read.xlsx("path/to/file.xlsx", sheetName = "Sheet1")
```

## Read from Salesforce

Many organisations utilisae a CRM for storing their customer focused data. This can be imported directly into R using the `RForcecom` package. This allows for queries written in SOQL (Salesforce Object Query Language) to be executed against Salesforce. Details regarding how to structure an SOQL query can be found here: `https://developer.salesforce.com/docs/atlas.en-us.soql_sosl.meta/soql_sosl/sforce_api_calls_soql_sosl_intro.htm`.

```{r, eval=FALSE}
library(RForcecom) # install.packages("RForcecom")

username <- ""
password <- ""
security_token <- ""

session <- rforcecom.login(username, paste0(password, security_token))

q <- "SELECT Id, Name FROM Account"

df <- rforcecom.query(session, q)
```